Growth Resilience (reanalisis)

### 2018-11-16 analysis/bai/analysis_resilience_bai.Rmd
change output figure resilience BAI
update bai hubers

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}
library("tidyverse")
library("dplR")
library("knitr")
library('gtable')
library('grid')
library('gridExtra')
library('stringr')
library('pander')
library('broom')
library('effects')
library('devtools')
# devtools::install_github("ajpelu/auxiliar")
library('car')
library('auxiliar')
library('WRS2')
library('MASS')
library('rcompanion')
```
# Resilience

@@

```{r}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep = '')

# sj 
sj <- read.rwl(fname=paste0(di, '/data_raw/dendro_ring/sn_sanjuan/sn_sanjuan.rwl'), format="tucson")

# canar 
ca <- read.rwl(fname=paste0(di, '/data_raw/dendro_ring/sn_canar/sn_canar.rwl'), format="tucson")

# Read diameters data
compete <- read.csv(file=paste0(di, '/data_raw/dendro_competence.csv'), header=TRUE, sep=',')
```

```{r}
source(paste0(di, 'script/R/rw_byTree.R'))
source(paste0(di, 'script/R/bai_piovesan.R'))
source(paste0(di, 'script/R/baiResilience.R'))
```

@@

write.csv(aux_coefs, file=paste0(di, '/out/correla_resilience/correla_window_size.csv'), row.names = F)
```

@@

# Export csv 
write.csv(g, file=paste0(di, 'data/resilience/crecimientos_drought.csv'), row.names = FALSE)

@@

pgrowht
ggsave(plot=pgrowht, width=8, height = 4,
       filename=paste0(di, 'out/fig/resilience/bai_events.pdf')) 
```

@@

# Export csv 
write.csv(re, file=paste0(di, 'data/resilience/resilience_bai.csv'), row.names = FALSE)
```

@@

```{r}
normtestA <- rbind(nrcA, nrtA, nrsA, nrrsA) 
normtestA %>% pander()
write.csv(normtestA, 
          file=paste0(di, '/out/anovas_resilience/bai/normo_disturb_year.csv'), row.names = F)
```

```{r}
normtestB <- rbind(nrcB, nrtB, nrsB, nrrsB) 
normtestB %>% pander()
write.csv(normtestB, 
          file=paste0(di, '/out/anovas_resilience/bai/normo_site.csv'), row.names = F)
```

```{r}
normtestAB <- rbind(nrcAB, nrtAB, nrsAB, nrrsAB) 
normtestAB %>% pander()
write.csv(normtestAB, 
          file=paste0(di, '/out/anovas_resilience/bai/normo_disturb_year_site.csv'), row.names = F)
```

@@

homo %>% pander()
write.csv(homo, 
          file=paste0(di, '/out/anovas_resilience/bai/homocedasticidad.csv'), row.names = F)
```

@@

homo_log %>% pander()
write.csv(homo_log, 
          file=paste0(di, '/out/anovas_resilience/bai/homocedasticidad_log.csv'), row.names = F)
```

@@

```{r, echo=FALSE}
pdf(paste0(di, '/out/mean_resilience/bai/interaction_plotsSE.pdf'), width=9, height = 9)
grid.arrange(plot_mdSE, plot_msSE, plot_mdsSE, ncol=3)
dev.off()

pdf(paste0(di, '/out/mean_resilience/bai/interaction_plotsCI.pdf'), width=9, height = 9)
grid.arrange(plot_mdCI, plot_msCI, plot_mdsCI, ncol=3)
dev.off()
```

@@

write.csv(aovas_coeff, file=paste0(di, '/out/anovas_resilience/bai/anovas_statistics.csv'), row.names = F)

@@

write.csv(aovas_model_summary, 
          file=paste0(di, '/out/anovas_resilience/bai/anovas_summary_modelos.csv'), row.names = F)

@@

pdf(paste0(di, 'out/resilience_robust/bai/robust_plot_bai_drought.pdf'), width=9, height = 9)
robust_plot_bai_drought 
dev.off()
```

@@

pdf(paste0(di, 'out/resilience_robust/bai/robust_plot_bai_site.pdf'), width=9, height = 9)
robust_plot_bai_site 
dev.off()
```

@@

```{r}
# Export data 
write.csv(mhuber, file=paste0(di, '/out/anovas_resilience/huber_bai/robust_mhuber.csv'), row.names = F)
write.csv(mhuber_agg, file=paste0(di, '/out/anovas_resilience/huber_bai/robust_mhuber_agg.csv'), row.names = F)
write.csv(mhuber_a, file=paste0(di, '/out/anovas_resilience/huber_bai/robust_mhuber_a.csv'), row.names = F)
write.csv(mhuber_agg_a, file=paste0(di, '/out/anovas_resilience/huber_bai/robust_mhuber_agg_a.csv'), row.names = F)
write.csv(mhuber_b, file=paste0(di, '/out/anovas_resilience/huber_bai/robust_mhuber_b.csv'), row.names = F)
write.csv(mhuber_agg_b, file=paste0(di, '/out/anovas_resilience/huber_bai/robust_mhuber_agg_b.csv'), row.names = F)

write.csv(pairwise, file=paste0(di, '/out/anovas_resilience/huber_bai/robust_pairwise.csv'), row.names = F)

write.csv(trimmedanovas, file=paste0(di, '/out/anovas_resilience/huber_bai/trimmed_anovas.csv'), row.names = F)
```

>>>>

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}
library("tidyverse")
library("dplR")
library("knitr")
library('gtable')
library('grid')
library('gridExtra')
library('stringr')
library('pander')
library('broom')
library('effects')
library('devtools')
# devtools::install_github("ajpelu/auxiliar")
library('car')
library('auxiliar')
library('WRS2')
library('MASS')
library('rcompanion')
library('here')
```
# Resilience

@@

```{r}
# machine <- 'ajpelu'
# machine <- 'ajpeluLap'
# di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep = '')

# sj 
sj <- read.rwl(fname=here::here('/data_raw/dendro_ring/sn_sanjuan','sn_sanjuan.rwl'), format="tucson")

# canar 
ca <- read.rwl(fname=here::here('/data_raw/dendro_ring/sn_canar', 'sn_canar.rwl'), format="tucson")

# Read diameters data
compete <- read.csv(file=here::here('/data_raw', 'dendro_competence.csv'), header=TRUE, sep=',')
```

```{r}
source(here::here('/script/R/', 'rw_byTree.R'))
source(here::here('/script/R/', 'bai_piovesan.R'))
source(here::here('/script/R/', 'baiResilience.R'))
```

@@

write.csv(aux_coefs, file=here::here('/out/correla_resilience', 'correla_window_size.csv'), row.names = F)
```

@@

# Export csv 
write.csv(g, file=here::here('/data/resilience', 'crecimientos_drought.csv'), row.names = FALSE)

@@

pgrowht
ggsave(plot=pgrowht, width=8, height = 4,
       filename=here::here('/out/mean_resilience/','bai_events.pdf')) 
```

@@

# Export csv 
write.csv(re, file=here::here('data/resilience/','resilience_bai.csv'), row.names = FALSE)
```

@@

```{r}
normtestA <- rbind(nrcA, nrtA, nrsA, nrrsA) 
normtestA %>% pander()
write.csv(normtestA, 
          file=here::here('/out/anovas_resilience/bai', 'normo_disturb_year.csv'), row.names = F)
```

```{r}
normtestB <- rbind(nrcB, nrtB, nrsB, nrrsB) 
normtestB %>% pander()
write.csv(normtestB, 
          file=here::here('/out/anovas_resilience/bai','normo_site.csv'), row.names = F)
```

```{r}
normtestAB <- rbind(nrcAB, nrtAB, nrsAB, nrrsAB) 
normtestAB %>% pander()
write.csv(normtestAB, 
          file=here::here('/out/anovas_resilience/bai', 'normo_disturb_year_site.csv'), row.names = F)
```

@@

homo %>% pander()
write.csv(homo, 
          file=here::here('/out/anovas_resilience/bai','homocedasticidad.csv'), row.names = F)
```

@@

homo_log %>% pander()
write.csv(homo_log, 
          file=here::here('/out/anovas_resilience/bai/','homocedasticidad_log.csv'), row.names = F)
```

@@

```{r, echo=FALSE}
pdf(here::here('/out/mean_resilience/bai','interaction_plotsSE.pdf'), width=9, height = 9)
grid.arrange(plot_mdSE, plot_msSE, plot_mdsSE, ncol=3)
dev.off()

pdf(here::here('/out/mean_resilience/bai','interaction_plotsCI.pdf'), width=9, height = 9)
grid.arrange(plot_mdCI, plot_msCI, plot_mdsCI, ncol=3)
dev.off()
```

@@

write.csv(aovas_coeff, file=here::here('/out/anovas_resilience/bai','anovas_statistics.csv'), row.names = F)

@@

write.csv(aovas_model_summary, 
          file=here::here('/out/anovas_resilience/bai','anovas_summary_modelos.csv'), row.names = F)

@@

pdf(here::here('out/resilience_robust/bai','robust_plot_bai_drought.pdf'), width=9, height = 9)
robust_plot_bai_drought 
dev.off()
```

@@

pdf(here::here('out/resilience_robust/bai','robust_plot_bai_site.pdf'), width=9, height = 9)
robust_plot_bai_site 
dev.off()
```

@@

```{r}
# Export data 
write.csv(mhuber, file=here::here('/out/anovas_resilience/huber_bai/','robust_mhuber.csv'), row.names = F)
write.csv(mhuber_agg, file=here::here('/out/anovas_resilience/huber_bai/','robust_mhuber_agg.csv'), row.names = F)
write.csv(mhuber_a, file=here::here('/out/anovas_resilience/huber_bai/','robust_mhuber_a.csv'), row.names = F)
write.csv(mhuber_agg_a, file=here::here('/out/anovas_resilience/huber_bai/','robust_mhuber_agg_a.csv'), row.names = F)
write.csv(mhuber_b, file=here::here('/out/anovas_resilience/huber_bai/','robust_mhuber_b.csv'), row.names = F)
write.csv(mhuber_agg_b, file=here::here('/out/anovas_resilience/huber_bai/','robust_mhuber_agg_b.csv'), row.names = F)

write.csv(pairwise, file=here::here('/out/anovas_resilience/huber_bai/','robust_pairwise.csv'), row.names = F)

write.csv(trimmedanovas, file=here::here('/out/anovas_resilience/huber_bai/','trimmed_anovas.csv'), row.names = F)
```
